Approximation as Differentiation

### 2025-06-18 main/first-order.tex
Tweak.

One might also like to allow the programmer to embed additional ``approximation points'' into composite
structures, by providing them with a \emph{lifting} monad $\synVar{L}$. Rather than the usual definition of
lists of natural numbers as $\mu\alpha.1 + \synVar{nat} \times \alpha$, one could then (within the language)
define a type of ``approximation lists'' $\mu\alpha.\synVar{L}\,(1 + \synVar{L}\,\synVar{nat} \times \alpha)$,
or perhaps a custom approximating version of multiplication $*_{\text{appr}}: \synVar{L}\,\synVar{nat} \times
\synVar{L}\,\synVar{nat} \to \synVar{L}\,\synVar{nat}$, expressible as
\[x *_{\text{appr}} y = \tmBind{x}{\tmFun{x'}{\syn{if}\;x' \equiv
0\;\syn{then}\;\tmReturn{0}\;\syn{else}\;\tmBind{y}{\tmFun{y'}{\tmReturn{x' * y'}}}}}\]

@@

To interpret the syntactic type constructor $\synVar{L}$, \todo{show how $\LatGal$ has a lifting monad.}

>>>>

One might also like to allow the programmer to embed additional ``approximation points'' into composite
structures, by providing them with a \emph{lifting} type constructor $\synVar{L}$. Rather than the usual
definition of lists of natural numbers as $\mu\alpha.1 + \synVar{nat} \times \alpha$, one could then (within
the language) define a type of ``approximation lists'' $\mu\alpha.\synVar{L}\,(1 + \synVar{L}\,\synVar{nat}
\times \alpha)$, or perhaps a custom approximating version of multiplication $*_{\text{appr}}:
\synVar{L}\,\synVar{nat} \times \synVar{L}\,\synVar{nat} \to \synVar{L}\,\synVar{nat}$, expressible as
\[x *_{\text{appr}} y = \tmBind{x}{\tmFun{x'}{\syn{if}\;x' \equiv
0\;\syn{then}\;\tmReturn{0}\;\syn{else}\;\tmBind{y}{\tmFun{y'}{\tmReturn{x' * y'}}}}}\]

@@

To interpret the syntactic type constructor $\synVar{L}$, we note that $\LatGal$ has a lifting monad
$\mathcal{L}$ which sends any bounded lattice $X = (X, \meet, \join, \top, \bot)$ to the lattice
$\mathcal{L}(X) = X_\bot$.
